Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-07-30 ms.tex
added an image comparing to a higher temp model.

We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
Also, we average ll available spectra from the Masuda reduction to increate the signal to noise.
The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
Interestingly, the median spectrum has weaker features than the individual spectrum, perhaps because it is variable but also it could be part of the median process.

@@

>>>>

We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
Also, we average ll available spectra from the Masuda reduction to increate the signal to noise.
The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.

@@

As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
The line ratios appear to match the BOSZ model with T=4500 K much better.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
\end{centering}
\end{figure}

This motivates a check on the temperatures, so we compare 3 models all with log(g)=4.5 and
